\documentclass[12pt]{cmuthesis}
\raggedbottom

%for a more compact document, add the option openany to avoid
%starting all chapters on odd numbered pages

\usepackage{comment}
\usepackage{xurl}
\usepackage{ifthen}
\usepackage{framed}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{times}
\usepackage{amssymb}
\usepackage[export]{adjustbox}
\usepackage{rotating}
\usepackage{times}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage[numbers]{natbib}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{algorithm2e}
\usepackage{float}

\SetAlgoSkip{bigskip}

% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Approximately 1" margins, more space on binding side
%\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar]{geometry}
%for general printing (not binding)
\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar,hmarginratio=1:1]{geometry}

% Add a border around captions
% from: https://tex.stackexchange.com/a/162830/155140
\makeatletter
\long\def\@makecaption#1#2{%
  \vskip\abovecaptionskip
  \sbox\@tempboxa{\fbox{#1: #2}}%
  \ifdim \wd\@tempboxa >\hsize
    \fbox{\parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{#1: #2}}\par
  \else
    \global \@minipagefalse
    \hb@xt@\hsize{\hfil\box\@tempboxa\hfil}%
  \fi
  \vskip\belowcaptionskip}
\makeatother

% Provides a draft mark at the top of the document.
% \draftstamp{\today}{DRAFT}

\begin{document}

\frontmatter

\title{{\bf Scaling Up Wearable Cognitive Assistance for Assembly Tasks}}
\author{Roger Iyengar}
\date{April 2023}
\Year{2023}
\trnumber{CMU-CS-23-112}

\vspace{3cm}

\committee{Mahadev Satyanarayanan (Satya) (Chair) \\
  Martial Hebert \\
  Roberta Klatzky \\
  Padmanabhan Pillai (Intel Labs)
}

\support{This research was sponsored by Autodesk, the National Science
  Foundation under
  award numbers 1518865 and 2106862, the NSF Graduate Research Fellowship under
  Grants DGE1252522 and DGE1745016, and the Defense Advanced Research Projects
  Agency under award number HR001117C0051.
}

\disclaimer{The views and conclusions contained in this document are those of
  the author
  and should not be interpreted as representing the official policies, either
  expressed or implied, of any sponsoring institution, the U.S. government or
  any other entity.
}

% copyright notice generated automatically from Year and author.
% permission added if \permission{} given.

\keywords{Wearable Cognitive Assistance, Wearable Computing, Edge Computing,
  Split Computing, Computer Vision, Synthetic Data
}

\maketitle

\begin{dedication}
  For Rajan Laddu, Sujeath Pareddy, and Joel Reidenberg.\\
  May your memories be a blessing.
\end{dedication}

\begin{abstract}
  Wearable Cognitive Assistance (WCA) applications run on wearable mobile
  devices, to provide guidance for real world tasks.
  Physical assembly tasks have been a significant focus of research on WCA.
  We introduce new techniques to support the development of WCA applications for
  more complex assembly tasks than previous techniques supported.
  In addition, our work reduces the load on developers creating WCA applications
  by eliminating the need to collect and label real training images.
  We accomplish this by training computer vision models on synthetically
  generated images.
  This dissertation investigates escalation to human experts in cases when a
  user is not satisfied with the automated guidance from an application.
  Lastly, we develop a new version of a software framework for WCA
  applications, and evaluate ways in which WCA applications can benefit from
  running computations directly on mobile devices.
\end{abstract}

\begin{acknowledgments}
  I am deeply indebted to my advisor Satya.
  Satya has taught me a lot about approaching difficult problems, conducting
  research, selling ideas, and communicating results.
  In addition, he has been a strong advocate for me and he has done a lot to
  help ensure my successful completion of the program.
  I also owe a great deal to the members of my thesis committee: Martial Hebert,
  Roberta Klatzky, and Padmanabhan Pillai.
  They have provided valuable guidance on this research, and helped improve the
  quality of this document.

  Satya's research group is an extremely collaborative environment, where
  people are always willing to help each other out.
  Thank you to Mihir Bala, Jim Blakley, Jason Choi, Tom Eiszler, Ziqiang Feng,
  Shilpa George, Jan Harkes, Chanh Nguyen, Eric Sturzinger, and Junjue Wang
  for making this such a productive and pleasant place to work.
  Additional thanks are due to Jan and Tom for managing and supporting all of
  our group's servers.

  I was fortunate enough to mentor Qifei Dong, Max Krieger, Di Wang, and Emily
  Zhang; all of whom contributed significantly to this work.
  I also had the privilege of being mentored by Professors Brendan Juba,
  Joe Near, Norman Sadeh, Dawn Song, and Sebastian Zimmeck prior to my work with
  Satya.
  I owe a debt of gratitude to my other research collaborators:
  Steven M. Bellovin, Sushain Cherivirala, Lorrie Cranor, Yuanyuan Feng, Hana
  Habib, Margaret Hagan, Bin Liu, Vinayshekhar Bannihatti Kumar, Namita Nisal,
  Truong An Pham, Joel Reidenberg, Michel Roy, Florian Schaub, Peter Story,
  Om Thakkar, Abhradeep Thakurta, Haithem Turki, Lun Wang, Ziqi Wang, Yu Xiao,
  Shomir Wilson, and Lieyong Zou.
  On top of this, I have benefited substantially from anonymous reviews of my
  papers.
  Additional thanks are due to the many teachers I have had throughout the
  course of my life.

  Thank you to Wael Darwich for your development work on A3D, for your work
  generating synthetic images, and for helping me get A3D set up to generate my
  own synthetic images.
  Haley Edie was instrumental in coordinating our collaboration with Autodesk,
  and getting me access to Autodesk resources.
  David Lovell ensured that the phone sanitizer parts were manufactured and
  shipped to us, and he captured some of our early test data.

  Rod Heiple handled the Autodesk collaboration on the CMU side.
  Ryan Bates 3D printed parts for the toy plane.
  Deb Cavlovich, Catherine Copetas, Sara Golembiewski, Connie Herold,
  Chase Klingensmith, Nichole Merritt, Colleen Mollenauer, and Linda Moreci
  provided fantastic administrative support and helped me navigate several
  bureaucratic processes.

  Writing software in the 21st century is standing on the shoulders of giants.
  This work would not have been possible without the developers of GNU, Linux,
  LLVM, Cuda, PyTorch, TensorFlow, Android, CPython, NumPy, SciPy, Matplotlib,
  OpenCV, CVAT, fish shell, Emacs, pudb, IntelliJ, Docker, AIOHTTP, Jupyter
  Notebook, ZeroMQ, and countless other software projects.

  Lastly, thank you to all of my family and friends,
  especially my parents Arun and Louise Iyengar.
  I would not be here without your love and support.
\end{acknowledgments}

\tableofcontents
\listoffigures
\listoftables
\mainmatter

%% Double space document for easy review:
%\renewcommand{\baselinestretch}{1.66}\normalsize

% The other requirements Catherine has:
%
%  - avoid large margins.  She wants the thesis to use fewer pages,
%    especially if it requires colour printing.
%
%  - The thesis should be formatted for double-sided printing.  This
%    means that all chapters, acknowledgements, table of contents, etc.
%    should start on odd numbered (right facing) pages.
%
%  - You need to use the department standard tech report title page.  I
%    have tried to ensure that the title page here conforms to this
%    standard.
%
%  - Use a nice serif font, such as Times Roman.  Sans serif looks bad.
%
% Other than that, just make it look good...

\include{intro}
\include{background}
\include{detection}
\include{synthetic}
\include{human}
\include{implementation}
\include{conclusion}

\backmatter

% By default \bibsection is \chapter*, but we really want this to show
% up in the table of contents and pdf bookmarks.
\renewcommand{\bibsection}{\chapter{\bibname}}

%\newcommand{\bibpreamble}{This text goes between the ``Bibliography''
% header and the actual list of references}

\bibliographystyle{plainnat}
\bibliography{thesis}

\end{document}
